Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Correct reference to supplementary figure

Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure \@ref(fig:evaluator-differences)).
However, the analyses did account for different raters for each article by including this as a random effect.

>>>>

Looking at the ratings for all 450 articles and given the differing number of articles each co-author evaluated, there was broad agreement with no discernible patterns showing a strong bias or cause for concern (Figure S1).
However, the analyses did account for different raters for each article by including this as a random effect.
